---
title: "Mindat Data"
author: "Xiang Que"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mindat Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Mindat Info

Note the various macros within the `vignette` section of the metadata block above. 

## Basical Objects

The `html_vignette` template includes a basic CSS theme. 
    output: 
      rmarkdown::html_vignette:
        css: mystyles.css


## Data structure

datasets are data frames made up of **rows** and **columns**. The columns are almost always labeled and the rows are sometimes labeled. The following code provides some data about an IMA_minerals in a format commonly seen in the wild. The table has three columns and four rows, and both rows and columns are labeled.

```{r}
library(OpenMindat)


```

### Data semantics

Some Descriptions 

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
#plot(1:10)

```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
