---
title: "OpenMindat"
author: "Xiang Que"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OpenMindat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Overview
Mindat.org is the world's largest open database of minerals, rocks, meteorites and the localities they come from.Mindat.org is run by the not-for-profit.

Learn  Learn more about rocks and minerals, their origins and their uses: [Enter our learning center](https://www.mindat.org/a/learn).

1.Rocks and Meteorites
2.Popular Minerals 

### Community
1.Photography  We have 1,280,073 photographs uploaded by our community.
2.Support us  We can't continue without your financial support. We are a 501(c)(3) non-profit
3.Events  Our calendar of important events for the mineral community.
4.Museums  Our directory of mineral museums and public collections worldwide.





```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(OpenMindat)
```


